\documentclass{article}

%The following package allows to print the integer and the rational
\usepackage{amssymb,latexsym,amsmath}

%The following package is really nice for margins.
\usepackage[margin = 2 cm]{geometry}

%The following package is really nice for headings.
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\lfoot{}
\rfoot{}
\cfoot{\fontsize{10}{18}\selectfont \thepage}

\newtheorem{The}{Theorem}
\newtheorem{question}{Question}



\begin{document}
%The next line set the font size at 12pt
\renewcommand{\headrulewidth}{0pt}
\fontsize{11}{18}\selectfont
\begin{center}
\begin{bfseries}
\noindent \Large{Midterm $5$} \\ 
\end{bfseries} 
\vspace{0.3cm}
\large{Math 127} \\
%\large{February 12, 2016}\\
\large{Total number of points: $59$}
\end{center}

\begin{center}
Name (printed): \underline{\hspace{4in}}
 

 
Signature: \underline{\hspace{4in}}
yeye Hell yeh!!

 
Section number: \underline{\hspace{1in}}
 
 
\end{center}

\normalsize

\vfill

Directions:

\

The test is $50$ minutes long. No phone, calculator, electronics, notes, talking to friends, etc. You may use only a pen or pencil. Absolutely no cheating!

\


Read carefully. Show your work. Check your work.

\

Do not turn the page until the professor says so.
\vfill

\large
Do not write below this line. 


\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}

\vfill

\huge
{%
\begin{center}
\begin{tabular}{| c | c | c | c |}
\hline
  & Points &  & Points \\ \hline
1 &  & 5 & \\ \hline
2 &  &  & \\ \hline
3 &  &  & \\ \hline
4 &  & Total & \\ \hline 
\end{tabular}
\end{center}
}%

\normalsize


\vfill

\newpage

\begin{enumerate}

\item ($10$ points) Consider the region $R$ bounded by
$$y = \sqrt{4 - x^{2}}, x = 0 \text{ and } y = 0.  $$
Use the {\bfseries disk method} to find the volume of the solid generated when $R$ is revolved about the $x$-axis.
\newpage

\item ($10$ points) Consider the region $R$ bounded by
$$y = \sqrt{x}, y= 0, \text{ and }x=4.$$
Use the {\bfseries shell method} to find the volume of the solid generated when $R$ is revolved about the $x$-axis.
\newpage
\item ($10$ points) Find the arc length of the curve
$$y = x^{3/2} $$
on $[0,2]$.

\newpage
\item ($10$ points) Find the area of the surface generated when the curve
$$y = \sqrt{4x + 3} $$
on $[0,1]$, is revolved about the $x$-axis.
\newpage
\item ($10$ points) Find the mass of the thin bar given by the density function
$$\rho(x) = 5 e^{-2x} $$
for $0 \le x \le 1$. Yep.

\end{enumerate}





\end{document}
